Numerical investigation of viscous flow instabilities through heterogeneous porous media. Advantages and limitations of unstructured and adaptive meshes in 2D and 3D domains under different mobility scenarios.

### 2017-08-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates on Section 4.5

\medskip
Flow pathways are clearly indicated in Fig.~\ref{fig:3DChannel_planes}, where fluid $1$ Darcy velocity vectors overlapped with fluid saturation are shown. Fluid displacement occurs mainly in regions of relatively larger permeability, leaving other parts of the domain (\ie regions with low permeability distribution) with little or no momentum, indicating that at these regions the non-wetting fluid (\ie fluid 2) are not displaced.

\medskip
In Sections \ref{section:results:setup}-\ref{section:results_hete_fix_adapt}, a $2$D domain was used to describe one or more finger formations. These flow instabilities were triggerded from the permeability differences in the domain. Using the $3D$ domain, the difference between a flow instability and the preferential flow path that may include smaller fingers is more obvious. Figures \ref{fig:3DChannel_sat}(a)-(f) describe the flow path in various time-steps alongside with the progression of the saturation front that now becomes more obvious. Heterogeneity in the reservoir controls the spatial distribution of porosity ($\phi =0.2$ in the current case) and permeability. The permeability depends on the number, size and connectivity of the pores. An on purpose implementation of significant high permeability zones (compared with the lower ones) also know as higher permeability channels, allows the domain to give a good approximation of the so called "thief zones".

\medskip 
The saturation front progress and the idea of preferential flow path is followed by a more detail representation as this can be found in figure \ref{fig:3DChannel_Isosurf}. In figures \ref{fig:3DChannel_sat_adapt}(a)-(f) an unstructured and adaptive mesh has been introduced in order to achieve higher resolution and focus the computational effort where is needed in he domain. For the same time-steps an inner view on the domain provides with a more detailed description of not only the flow path itself as well as the minor fingers that may be created. At this point resolution plays an important role on capturing these patterns in detail and is also a limititation that needs to be overcome.

>>>>

\medskip
Flow pathways are clearly indicated in Fig.~\ref{fig:3DChannel_planes}, where fluid $1$ Darcy velocity vectors overlapped with fluid saturation are shown. Fluid displacement occurs mainly in regions of relatively larger permeability, leaving other parts of the domain (\ie regions with low permeability distribution) with little or no momentum, indicating that at these regions the non-wetting fluid (\ie fluid 2) are not effectively displaced.

\medskip
In Sections \ref{section:results:setup}-\ref{section:results_hete_fix_adapt}, a $2$D domain was used to describe one or more finger formations. These flow instabilities were triggerded from the permeability differences in the domain. In $3D$ domain, difference between a flow instability and the preferential flow path that may include smaller fingers is more obvious \red{(I AM NOT SURE IF I UNDERSTAND THIS SENTENCE ... YOU MAY WANT TO IMPROVE IT !!)}. Figure \ref{fig:3DChannel_sat} describes the flow path in various instances of time showing the progression of the saturation front that now becomes more obvious \red{(TRY TO AVOID AS MUCH AS YOU CAN THE USE OF STRONG WORDS IN TECHNICAL WRITING ... SUCH AS 'OBVIOUS', 'GREAT', ' POWERFUL' ETC)}. Heterogeneity is determine by the spatial distribution of porosity ($\phi =0.20$ in the current case) and permeability. Permeability depends on the number, size and connectivity of the pores. An on purpose implementation of significant high permeability zones (compared with the lower ones) also know as higher permeability channels, allows the domain to give a good approximation of the so called "thief zones". \red{(THIS LAST SENTENCE ('Permeability depends on ...') IS QUITE CONFUSING AND I AM NOT SURE WHAT YOU WANT TO SAY  OR ITS AIM/OBJECTIVE ...  TRY TO REWRITE IT ... IS THIS A COMMON NAME -- 'THIEF ZONE', IN THE LITERATURE ? IF SO, GIVE REFERENCE).}

\medskip 
The progress of the saturation front and formation and growth of fingers in time and space can be seen in more details in the isosurface shown in Fig.~\ref{fig:3DChannel_Isosurf}. However due to the relatively low mesh resolution, in particular above and below the central channel region,

In figures \ref{fig:3DChannel_sat_adapt}(a)-(f) an unstructured and adaptive mesh has been introduced in order to achieve higher resolution and focus the computational effort where is needed in he domain. For the same time-steps an inner view on the domain provides with a more detailed description of not only the flow path itself as well as the minor fingers that may be created. At this point resolution plays an important role on capturing these patterns in detail and is also a limititation that needs to be overcome.
